\hl{On the use of Generative adversarial neural networks for computing photonic crystal fiber optical properties}

### 2020-04-09 docs/paper/paper.tex
* Small fixes

\begin{table*}
	\centering
	\begin{tabular}{l|l|l|l}
		\textbf{Parameter} & \textbf{Generator} & \textbf{Critic} & \textbf{Regressor} \\\hline
		Hidden layers & 5 & 5 & 6 \\
		Neurons in hidden layers & $ 2^{2}~batchsize $ & $2^{layers}~batchsize$ & 50 \\
		Activation function & ReLU & Leaky ReLU & ReLU \\
		Optimizer & Adam \cite{kingma2014adam} & Adam & Adam \\
		Input normalization & Z-score & Z-score & Z-score \\
		Layer normalization & - & Batch \cite{ioffe2015batch} & Batch \\
		Loss function & MSE & MSE & MSE \\
	\end{tabular}
	\caption{Details of ANN models}
	\label{tbl:anndetails}
\end{table*}

@@

We have performed \hl{this and that experiments} which are discussed in the following sections.

>>>>

\begin{table*}
	\centering
	\begin{tabular}{l|l|l|l}
		\textbf{Parameter} & \textbf{Generator} & \textbf{Critic} & \textbf{Regressor} \\\hline
		Hidden layers & 5 & 5 & 6 \\
		Neurons in hidden layers & $ 2^{2}~batchsize $ & $2^{layers}~batchsize$ & 50 \\
		Activation function & ReLU & Leaky ReLU & ReLU \\
		Optimizer & Adam \cite{kingma2014adam} & Adam & Adam \\
		Input normalization & None & Z-score (for collected samples) & Z-score \\
		Layer normalization & - & Batch \cite{ioffe2015batch} & Batch \\
		Loss function & -Critic(generated) & Critic(generated) - Critic(collected) & MSE \\
	\end{tabular}
	\caption{Details of ANN models}
	\label{tbl:anndetails}
\end{table*}

@@

In the following subsections, we have performed experiments to show the performance of the base ANN system by its own comparing with the state-of-the-art method in the literature, improvement gained by employing GAN phase, and finally the computational cost of the overall system compared to the simulator. All numeric comparison results are average of 10 executions.
